Data Preparation

### 2023-03-23 x_data-crunching.qmd
initialise milestione table for arrivals

```{r}
source("./R/osn_dumps.R")
source("./R/osn_read_tardump.R")
source("./R/osn_make_nice_names.R")
source("./R/coerce_meter_to_feet.R")
```

@@

rwy_centerline_ls <- cast_rwy_ctr_line_ls(rwys_egll)
rwy_box           <- airport_threshold_box(rwys_egll)
airport_box       <- airport_centerline_box(rwys_egll)
```

@@

Address[which(LeastNEmployees == max(LeastNEmployees))]

@@

```{r}
rq <- ds |> 
  filter(ICAO24 %in% seen_at_airport$ICAO24) |> 
  coerce_unixepoch_to_datetime() |> 
  identify_trajectory_legs() |> 
  Alt_Outlier_filter(.alt_var = ALT_B) |> 
  fix_altitude_heuristic() |> 
  mutate(UID = paste(ICAO24, LEG, sep = "-"))
rq <- rq |> ungroup()

# check one more time for airport
seen_at_airport2 <- icao24_in_polygon(rq, airport_box, UID) |> 
  heuristic_DAO()
seen_at_airport2
```

@@

>>>>

```{r}
source("./R/osn_dumps.R")
source("./R/osn_read_tardump.R")
source("./R/osn_make_nice_names.R")
source("./R/coerce_meter_to_feet.R")
source("./R/altitude_outlier_filter.R")
source("./R/trj_fix_altitude.R")
source("./R/spatial_subset_jormungand.R")
```

@@

rwy_centerline_ls <- cast_rwy_ctr_line_ls(rwys_egll)
rwy_box           <- airport_threshold_box(rwys_egll)
airport_box       <- airport_centerline_box(rwys_egll)

# for later
jormungand <- trrrj::polygon_at_distance(c(arp_egll$LON, arp_egll$LAT), d = 205) |> 
  sf::st_as_sf() |> rename(geometry = x) |> mutate(NAME = "EGLL-205")
```

@@

@@

```{r}
rq <- ds |> 
  # subset for ICAO24s seen at the study airport
  filter(ICAO24 %in% seen_at_airport$ICAO24) |> 
  spatial_subset_jormungand(jormungand) |> 
  # human readable TIME
  coerce_unixepoch_to_datetime() |>
  # clean ALT and trim for airborne part with heuristic fix
  Alt_Outlier_filter(.alt_var = ALT_B) |> 
  fix_altitude_heuristic() |> 
  # assign leg for each airborne segment
  identify_trajectory_legs() |> 
  # force single FLTID here to construct niche UIDs
  group_by(ICAO24, LEG) |> fix_invalid_fltid() |> ungroup() |> 
  # construct UID
  mutate(UID = paste(ICAO24, LEG, sep = "-"))

# check one more time for airport
seen_at_airport2 <- icao24_in_polygon(rq |> sf::st_drop_geometry(), airport_box, UID) |> 
  heuristic_DAO()
seen_at_airport2
```

@@

per arrival trajectory (iterate, group modify)

* subset to 200NM (done - jormungand)
```{r}
fig <- ggplot() + geom_sf(data = arr_trjs |> cast_pts_to_ls(.group_var = UID)) +
  labs(subtitle = paste("EGLL arrivals", ptn, sep = "-")) +
  theme(plot.title.position = "plot")
#ggsave(plot = fig, filename = "./figures/EGLL-arrivals-single-day.png", dpi = 300, height = 5, width = 5)
fig
```

* initialise mst (done - initialise milestone table function on filtered trajectories)
* assign landing runway & landing time
* calculate characteristics
  + time-to-go
  + distance-to-go
  + crossings (e.g for ASMA)

* save out mst/enriched trajectory

```{r}
source("~/RProjects/paper-2023-ICNS/R/milestone_functions.R")
arr_trjs <- rq |> filter(UID %in% (seen_at_airport2 |> filter(DAO == "A") |> pull(UID)) )
mst <- initialise_milestone_table(arr_trjs)
mst
```
